Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards

### 2024-04-24 paper/paper.qmd
added discussion

## Price trend ratio to player average

@@

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

@@

Weaknesses and next steps should also be included. More player should be added into this analysis and

>>>>

@@

## Overall price trend

The player's performance does not have too much of a prediction factor in the price of their card. Overall, almost every player has a downward trend in price regardless of how they are performing in the league. I think this has to do with the initial overvaluation of the card. The quantity that is released into the market also plays a critical role in the price. As we know, the more supply, and if the demand can’t keep up with the supply, then the price will go down. With more packs of cards being opened every day, the number of cards being released into the market also increases.

## Confounding variables
The linear model may be too simple due to each player's positions and playstyles. Because we are assuming that the higher the statistics are the better a player is performing. However, basketball is not only about statistics. If a player is known and in charge of defensive plays, their blocks and rebounds may be more important compared to attack-oriented players. The behavior of a player outside the league is also very crucial in terms of this. Even though Ja Morant played well in the league, he had multiple occasions where he displayed illegal objects during his livestream on Instagram. This devastated his reputation overall and he also received game restrictions as punishment. His card price also plummeted from around 2000 to now at around 400 dollars.

@@

Since there isn’t a major platform that provides the tracking of every transaction of a card, it is very difficult to obtain the true price of the card. Sportscardpro only gathers its data from completed transactions of that card on eBay, which is only a portion of the sales that happen on the internet. Transactions of the card that often happen offline in stores are also not tracked, if I sold a card to my friend for a cheaper price, it is not reflected in the dataset from Sportscardpro.

Future steps would include categorizing each player based on their positions and giving weight to the statistics that would have a better indication of their performance. For example, giving more weight to the average number of blocks per game for defensive players. Another step would be the incorporation of other models to find better fits, because of the complex relationship between the price and the player statistics, a more sophisticated model may be needed.
